On the combination of Set Functions and Failures

### 2014-10-16 docs/src/usage.tex
:set path now stores absolute path names
Bug in ":add" command fixed, path handling improved

\item[\fbox{\code{:edit $file$}}]\pindex{:edit}
Load file $file$ into a text editor which is defined
as in the command \ccode{:edit}.

@@

\item[\fbox{\code{:show $m$}}]\pindex{:show}
Show the source text of module $m$ which must be accessible
via the current load path.

@@

>>>>

\item[\fbox{\code{:edit $m$}}]\pindex{:edit}
Load the source text of module $m$ (which must be accessible
via the current load path if no path specification is given)
into a text editor which is defined
as in the command \ccode{:edit}.

@@

\item[\fbox{\code{:show $m$}}]\pindex{:show}
Show the source text of module $m$ which must be accessible
via the current load path if no path specification is given.

@@

The path is a list of directories separated by \ccode{:}.
The prefix \ccode{\char126} is replaced by the home directory as
in the following example:
\begin{curry}
:set path aux:~/tests
\end{curry}
Relative directory names are replaced by absolute ones
so that the path is independent of later changes of the
current working directory.
